---
title: "Final"
author: "Sinha"
date: '2022-05-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
require(dplyr)
require(ggplot2)
require(lubridate)
require(tibble)
require(reshape2)
require(scales)
```


The variables that would be used in the project are:
● Date in MM-DD-YYYY
● Day of the Week
● Quarter : A portion of the month. A month was divided into four quarters
● Department : Associated department with the instance
● Number of workers : Number of workers in each team
● Number of Style Change : Number of changes in the style of a particular product
● Targeted Productivity : Targeted productivity set by the Authority for each team for each
day.
● SMV : Standard Minute Value, it is the allocated time for a task
● WIP : Work in progress. Includes the number of unfinished items for products
● Overtime : Represents the amount of overtime by each team in minutes
● Incentive : Represents the amount of financial incentive (in BDT) that enables or
motivates a particular course of action.
● Idle time : The amount of time when the production was interrupted due to several
reasons
● Idlemen : The number of workers who were idle due to production interruption
● Actual productivity : The actual % of productivity that was delivered by the workers. It
ranges from 0-1.


```{r}
garmentpro <- read.csv("C:/Users/sinha/Downloads/garments_worker_productivity - garments_worker_productivity (2).csv")


garmentpro$date <- mdy(garmentpro$date)

garmentpro <- mutate(garmentpro, difference = actual_productivity - targeted_productivity)
garmentpro[is.na(garmentpro)] = 0
garmentpro$idle_time <- as.integer(garmentpro$idle_time)

garmentpro$department <- gsub("sweing", "sewing", garmentpro$department)

head(garmentpro)

```
```{r}
str(garmentpro)
```

# Calculating mean targeted and actual productivity for each day of each department and visualizing the data with line graphs.

```{r}
gar <- data.frame(garmentpro %>%
                    group_by(date) %>%
                    filter(department == "sewing") %>%
                    summarise(mean_tar = mean(targeted_productivity), mean_act = mean(actual_productivity)))
gar1 <- data.frame(garmentpro %>%
                    group_by(date) %>%
                    filter(department == "finishing") %>%
                    summarise(mean_tar = mean(targeted_productivity), mean_act = mean(actual_productivity)))

head(gar)
head(gar1)
```

```{r}
colors <- c("Mean Targeted Productivity" = "blue", "Mean Actual Productivity" = "darkred")

ggplot(gar, aes(x=date)) + 
  geom_line(aes(y = mean_tar, color = "Mean Targeted Productivity"), group = 1, lwd = 0.75) + 
  geom_line(aes(y = mean_act, color="Mean Actual Productivity"), group = 1, lwd = 0.75) +
  labs(x = "Date", y = "Mean productivity")+
  scale_color_manual(values = colors) +
  ggtitle("Sewing Department")

ggplot(gar1, aes(x=date)) + 
  geom_line(aes(y = mean_tar, color = "Mean Targeted Productivity"), group = 1, lwd = 0.75) + 
  geom_line(aes(y = mean_act, color="Mean Actual Productivity"), group = 1, lwd = 0.75) +
  labs(x = "Date", y = "Mean productivity")+
  scale_color_manual(values = colors)+
  ggtitle("Finishing Department")
```



```{r}
sewing <- data.frame(garmentpro %>%
                       
                       filter(department == "sewing"))

finishing <- data.frame(garmentpro %>%
                          filter(department == "finishing"))



```

```{r}
ggplot(garmentpro, aes(x=idle_men, fill=department))+
  geom_bar() + facet_grid(.~department) + xlab("Idle Time")

ggplot(garmentpro, aes(x=idle_time, fill=department))+
  geom_bar(width = 5) + facet_grid(.~department) + xlab("Idle Time")
```

The graphs above shows that the variables 'idle-men' and 'idle_time' consists '0' as their values so these two variables would not be used in Multiple Linear Regression.

# Multiple Linear Regression for Sewing

```{r}
fit = lm(difference ~ quarter + day + smv + wip + over_time + incentive + no_of_style_change + no_of_workers, data = sewing)

summary(fit)
```
Eliminating quarter

```{r}
fit = lm(difference ~ day+smv + wip + over_time + incentive + no_of_style_change + no_of_workers, data = sewing)

summary(fit)
```
Eliminating wip 
```{r}
fit = lm(difference ~ day++ smv + over_time + incentive + no_of_style_change + no_of_workers, data = sewing)

summary(fit)
```
Eliminating over_time

```{r}
fit = lm(difference ~ day++ smv + incentive + no_of_style_change + no_of_workers, data = sewing)

summary(fit)
```
Eliminating day

```{r}
fit = lm(difference ~ smv + incentive + no_of_style_change + no_of_workers, data = sewing)

summary(fit)
```
Eliminating no_of_style_change
```{r}
fit = lm(difference ~ smv + incentive + no_of_workers, data = sewing)

summary(fit)
```

The variables left are Standard Minute value (smv), Incentive and No_of_workers. There are variables that have significant effect on the variation of response variable 'difference'.

# Multiple Linear Regression for finishing

```{r}
fit = lm(difference ~ quarter + day + smv + wip + over_time + incentive + no_of_style_change + no_of_workers, data = finishing)

summary(fit)
```
Eliminating wip and no_of_style_change
```{r}
fit = lm(difference ~ quarter + day + smv + over_time + incentive + no_of_workers, data = finishing)

summary(fit)
```
Eliminating day
```{r}
fit = lm(difference ~ quarter + smv + over_time + incentive + no_of_workers, data = finishing)

summary(fit)
```
Eliminating incentive
```{r}
fit = lm(difference ~ quarter + smv + over_time + no_of_workers, data = finishing)

summary(fit)
```
Eliminating quarter
```{r}
fit = lm(difference ~ smv + over_time + no_of_workers, data = finishing)

summary(fit)
```

The variables left are Standard Minute value (smv), Overtime and No_of_workers. There are variables that have significant effect on the variation of response variable 'difference'.

# Finding correlation between these significant variables that would be used to provide useful information about the forthcoming graphs in this file.

```{r}
cor(garmentpro[garmentpro$department == "sewing", c("no_of_workers", "difference","smv","incentive")])
cor(garmentpro[garmentpro$department == "finishing", c("no_of_workers", "difference","smv","over_time")])
```

# Visualizing relationship between Number of Workers and Difference in Productivity 

```{r}

ggplot(garmentpro,aes(x=no_of_workers, 
             y=difference, 
             color=department))+
  geom_point()+
  geom_smooth(formula = y ~ x, method = "lm")+ ggtitle("Number of Workers vs. Difference in Productivity", subtitle = "Sewing: r = 0.0774, Finishing: r = 0.263") + xlab("Number of Workers") + ylab("Difference in productivity")


xdensity <- ggplot(garmentpro, aes(x= no_of_workers, fill=department)) + 
  geom_density(alpha=.5) + 
  scale_fill_manual(values = c('red','lightblue')) + 
  theme(legend.position = "none")+ ggtitle("Number of Workers vs. Difference in Productivity") + xlab("Number of Workers") + ylab("Density of distribution of x values")


xdensity

```

The x density curve above show that Finishing department has less number of workers in each team in comparison to that of sewing department.

# Visualizing relationship between Standard Minute Value(smv) and Difference in Productivity 

```{r}
ggplot(garmentpro,aes(x=smv, 
             y=difference, 
             color=department))+
  geom_point()+
  geom_smooth(formula = y ~ x, method = "lm") + ggtitle("Standard Minute value vs. Difference in Productivity", subtitle = "Sewing: r = -0.194, Finishing: r = 0.215") + xlab("Standard Minute Value (smv)") + ylab("Difference in productivity")


xdensity <- ggplot(garmentpro, aes(x= smv, fill=department)) + 
  geom_density(alpha=.5) + 
  scale_fill_manual(values = c('red','lightblue')) + 
  theme(legend.position = "none") + ggtitle("Standard Minute value vs. Difference in Productivity") + xlab("Standard Minute Value (smv)") + ylab("Density of distribution of x values")


xdensity
```

The x density curve above show that Finishing department has less allocated time for a task in comparison to that of sewing department.

# Visualizing the other relationships:

```{r}
ggplot(sewing,aes(x=incentive, 
             y=difference))+
  geom_point(color = "darkred")+
  geom_smooth(formula = y ~ x, method = "lm") + ggtitle("SEWING: Financial Incentive vs. Difference in Productivity, r = 0.674") + xlab("Financial Incentive") + ylab("Difference in productivity")

ggplot(finishing,aes(x=over_time, 
             y=difference))+
  geom_point(color="steelblue")+
  geom_smooth(formula = y ~ x, method = "lm") + ggtitle("FINISHING: Overtime vs. Difference in Productivity, r = 0.046") + xlab("Overtime") + ylab("Difference in productivity")


```

Results:

Multiple significant relationships were found between difference in productivity and Sewing department: (p<0.001, F= 218.8 on 3 and 687 DF, Adjusted R-squared:  0.4864 ), Finishing department: (p<0.001, F=22.94 on 3 and 502 DF,  Adjusted R-squared:  0.1153 )

The predicted linear models:

Sewing:

Difference = {- 74.4  - 3.61(smv) + 2.5(incentive) + 1.85(no_of_workers)} 10^(-3)

Finishing:

Difference = {- 34360 + 6083(smv) - 2.363(over_time) + 1841(no_of_workers)} 10^(-5)

Explanation:

For sewing department, the financial ‘incentive’, the allocated work time ‘smv’ and the number of workers all have statistically significant effect on the difference between productivities. Roughly 49% of the variability in difference is accounted for by a multiple linear model with these four variables (R2 Adj = 0.4973).

For finishing department, the ‘overtime’ worked by employees, the
allocated work time ‘smv’ and the number of workers statistically significant effect on the difference between productivities. Roughly 11.5% of the variability in difference is accounted for by a multiple linear model with these three variables (R2 Adj = 0.1153).
